COG-ED Manuscript

### 2022-01-04 06_Paper/COG-ED/Manuscript.Rmd
corrected typos

Increases in subjective task load were investigated for each NASA-TLX subscale, now including 1-back.
Ratings on the mental load and effort subscales increased between all n-back levels ($p<.001$) except between 3- and 4-back.
Ratings on the physical load and the performance subscales only increased between 1- and 3-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X3`, and `r`apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X3`, respectively) and 1- and 4-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X4`, and`r `apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X4`, respectively).
Ratings on the frustration and time pressure subscales increased between all n-back levels ($p<.001$) except between 1- and 2-back and 3- and 4-back.
Overall, these ratings showed that the increase in task load was being perceived as such.

>>>>

Increases in subjective task load were investigated for each NASA-TLX subscale, now including 1-back.
Ratings on the mental load and effort subscales increased between all n-back levels ($p<.001$) except between 3- and 4-back.
Ratings on the physical load and the performance subscales only differed between 1- and 3-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X3`, and `r apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X3`, respectively) and 1- and 4-back (`r apa_print(hypothesis1c_physical_contrasts)$statistic$X1_X4`, and `r `apa_print(hypothesis1c_performance_contrasts)$statistic$X1_X4`, respectively).
Ratings on the frustration and time pressure subscales increased between all n-back levels ($p<.001$) except between 1- and 2-back and 3- and 4-back.
Overall, these ratings showed that the increase in task load was being perceived as such.
